Miscellaneous notes for D. Huybrechts's Complex Geometry

### 2016-09-29 Complex Geometry - index/misc/complex geometry-misc.tex
Correcting error in complex geometry-misc. Initiating new notes on a conference: connecting few and many body pictures of FQH.

\maketitle
\abstract{
Miscellaneous notes for D. Huybrechts's book \textit{Introduction
to Complex Geometry}, include some homeworks done.
}
\tableofcontents
\section{The structure of almost complex structures on \texorpdfstring{$\mathbb{R}^{4}$}{}
  (exercise 1.2.1)}
\label{sec:The_structure_of_almost_complex_structures_on_R2n}
In exercise 1.2.1, it says that the set of all compatible almost complex
structures on a euclidean space of dimension $2n$, is two copies of $S^2$.

@@

@@

        \begin{proof}
            The $\phi$ is construct as follows. Let 
            $J_0=\left( \begin{array}{cc}
                 0 & -1 \\
            1 & 0 \\ \end{array} \right)$, define $H(x+iy)$ for
            $x,y\in \mathbb{R}$ as
            \begin{align}
                H(x+iy) = x I + y J
            \end{align}
            Then:
            \begin{align}
                \phi(A)_{ij} \equiv H(a_{ij})
            \end{align}
            Then:
            \begin{align}
                \phi(i) = \left( \begin{array}{ccc}
                     J & 0 & 0 \\
                     0 & \text{...} & 0 \\
                     0 & 0 & J \\
                    \end{array} \right)
            \end{align}
            By direct simple calculation (remember to use the technique
            of block multiplication), we have:
            $\phi(i B)= \phi(i)\phi(B)$.
            for any $B\in \mathrm{GL}(n,\mathbb{C}$. This shows also
            $BJB^{-1}=J$, since $iB=Bi$.

@@

        To understand that post \cite{math.se_1}, I also read this
        \cite{math.se_2}. In it, it asks how to prove that 
        \begin{align}
            \label{eq:sec.1.1.2_why_glnc_injectInto_positive_comp}
            GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})
        \end{align}
        for any $n$. The questioner gives the intuition for this fact:
        \begin{quote}
            how about since as Lie groups, $GL(n,\mathbb{C}) 
            \subset GL(2n, \mathbb{R})$ and $GL(n,\mathbb{C})$ is connected 
            but $GL(2n, \mathbb{R})$ has two connected components, one for 
            positive determinant and one for negative determinant? And the 
            identity has positive determinant, so it must lie in that 
            component.
        \end{quote}

@@

        \end{quote}

>>>>

\maketitle
\abstract{
Miscellaneous notes for D. Huybrechts's book \textit{Introduction
to Complex Geometry}, include some homeworks done.
}
\tableofcontents
\section{The structure of almost complex structures on \texorpdfstring{$\mathbb{R}^{4}$}{}
  (exercise 1.2.1)}
\label{sec:The_structure_of_almost_complex_structures_on_R2n}
In exercise 1.2.1, it says that the set of all compatible almost complex
structures on a euclidean space of dimension $4$, is two copies of $S^2$.

@@

        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}

@@

        \begin{proof}
            The $\phi$ is construct as follows. Let 
            $J_0=\left( \begin{array}{cc}
                 0 & -1 \\
            1 & 0 \\ \end{array} \right)$, define $H(x+iy)$ for
            $x,y\in \mathbb{R}$ as
            \begin{align}
                H(x+iy) = x I + y J
            \end{align}
            Then:
            \begin{align}
                \phi(A)_{ij} \equiv H(a_{ij})
            \end{align}
            Then:
            \begin{align}
                \phi(i) = \left( \begin{array}{ccc}
                     J & 0 & 0 \\
                     0 & \text{...} & 0 \\
                     0 & 0 & J \\
                    \end{array} \right)
            \end{align}
            By direct simple calculation (remember to use the technique
            of block multiplication), we have:
            $\phi(i B)= \phi(i)\phi(B)$.
            for any $B\in \mathrm{GL}(n,\mathbb{C})$. This also shows 
            $BJB^{-1}=J$, since $iB=Bi$.

@@

        To understand that post \cite{math.se_1}, I also read this
        \cite{math.se_2}. In it, it asks how to prove that 
        \begin{align}
            \label{eq:sec.1.1.2_why_glnc_injectInto_positive_comp}
            GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})
        \end{align}
        for any $n$. The questioner gives the intuition for this fact:
        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}

        \begin{quote}
            how about since as Lie groups, $GL(n,\mathbb{C}) 
            \subset GL(2n, \mathbb{R})$ and $GL(n,\mathbb{C})$ is connected 
            but $GL(2n, \mathbb{R})$ has two connected components, one for 
            positive determinant and one for negative determinant? And the 
            identity has positive determinant, so it must lie in that 
            component.
        \end{quote}
        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}

@@

        \end{quote}
        \begin{center}\noindent\rule{8cm}{0.4pt}\end{center}
